\texttt{\texttt{NeuralNetworkVisualization}}

### 2019-09-22 paper_neural_network.Rmd
modified paragraph

Neural networks have some useful properties, including: Neural networks have the ability to learn and model non-linear and complex relationships, useful for tackling real-life problems. Furthermore, they can generalize after learning from inputs, they can infer unnoticed relationships on unseen data. Thereby, the model can generalize and predict on unknown data. Lastly, these models also do not impose any restrictions on the input variables, allowing for greater flexibility. In addition, they appear to deal better with heteroskedasticity [@Haykin.2009].

>>>>

Neural networks have some useful properties, including: Neural networks are able to learn and model non-linear and complex relationships, useful for tackling real-life problems. Also, they can generalize after learning from inputs, thus infer unnoticed relationships on unseen data. Thereby, the model can generalize and predict on unknown data. Lastly, these models also do not impose any restrictions on the input variables, allowing for greater flexibility. In addition, they appear to deal better with heteroskedasticity [@Haykin.2009].
